\cvsection{Other Employment}

\begin{cventries}

\cventry
  {Musician} % job title
  {Australian Army Reserves} % organization
  {} % location
  {2010 - Present} % date(s)
{%
\begin{itemize}
  \item Undertook ceremonial activities including bugling at dawn services.
  \item Provide entertainment during Army functions.
  \item Be the public face of the Army at public events including sporting matches.
\end{itemize}
\textbf{Achievements}
\begin{itemize}
  \item Directed, Filmed and Edited viral music videos;
    \chref{https://youtu.be/U7LAo9klSRk}{\emph{I Was Only 19}} watched by over 300\~000 people on ANZAC Day in 2015,
    and \chref{https://www.facebook.com/thelancerband/videos/1420565134653508/}{\emph{When the War Is Over}} watched by over 700\~000 people on ANZAC Day in 2017.
  \item Selected as bugler to perform in the Centenary of ANZAC commemorations in Poziéres (France) and Polygon Wood.
  \item Best Bandsperson 2016.
\end{itemize}
}

\cventry
  {\nth{1} Year Demonstrator} % job title
  {School of Chemistry, The University of Sydney} % organization
  {} % location
  {2014 - 2016} % date(s)
{%
  \begin{itemize}
    \item Ensure the safety and safe work practices
      of \nth{1} year students under his supervision.
    \item Communicate complex scientific ideas
      in a fun, engaging, and interactive manner.
  \end{itemize}
}

\cventry
  {Year in Industry Student} % job title
  {Australian Sports Drug Testing Laboratory, National Measurement Institute} % organization
  {} % location
  {2012 - 2013} % date(s)
{%
  \begin{itemize}
    \item Developed proof of concept workflow for incorporating Machine
      Learning in anti-doping efforts.
    \item Validated the analytical measurement of small peptides in urine samples.
    \item Responsible for operation and maintenance of a nano-HPLC-MS-HRMS instrument.
    \item Moved and accounted for over 10 000 samples of urine.
  \end{itemize}
}

\end{cventries}
