\input{../preamble.tex}


%\recipient{<Company>}{<Address>}
\recipient{~}{~}
\date{\today}
\opening{Dear Joel,}
\closing{Regards,}

\begin{document}

\makelettertitle

I am writing to apply for the position of Junior Data Scientist as advertised on Seek.com. This position suits my skills in programming, data analysis, and data visualisation.

I have recently completed my Bachelor of Science with Honours, graduating with majors in both Computational Science and Chemistry and \nth{1} class Honours. During my Honours year I worked on the simulation of simple systems over long time scales, generating large volumes of data which I then had to analyse and extract useful information. This data extraction utilised a variety of techniques including statistical analysis and many forms of data visualisation including time dependent animations. This project was chosen to make use of the mathematical and computational analysis tools, including machine learning and parallel computing developed in my Computational Science Major with the knowledge of chemical systems and their behaviour from my Chemistry Major.

I was working on a new type of chemical system and so to perform the data analysis and visualisation I had to write all the code. The majority of the code for the data analysis was written in C++ (\href{https://github.com/malramsay64/analysis}{github.com/malramsay64/analysis}) utilising the flexibility and abstraction of an Object Oriented language while also having little computational overheads to efficiently analyse the vast quantities of data. The data visualisation was then performed primarily using Gnuplot (\href{https://github.com/malramsay64/Molecular-Crystals}{github.com/malramsay64/Molecular-Crystals}), though with much of the automation being performed using Python.

My Honours year also assisted in the honing of my presentation skills. During the year I was working as a \nth{1} Year Demonstrator, requiring me to communicate safety information, the experimental procedure, and skills required for the experiment. I was demonstrating the same experiment each week with a new group of students, allowing me to experiment with different methods of presenting the same information and evaluating how receptive the students were to the information. This testing I performed with the students was also helpful in designing presentations on my research, culminating in an assessed presentation on my Thesis which was strongly received.

The environment I was working in during my Honours year was fast paced, having a Thesis due with a deadline required quick development and implementation of code, quickly developing new data analysis tools and visualisations to investigate new properties of the simulated system.

I thank you for considering my application and look forward to hearing from you.

\makeletterclosing

\end{document}
