\input{../preamble.tex}


%\recipient{<Company>}{<Address>}
\recipient{~}{~}
\date{\today}
\opening{Dear Sir/Madam,}
\closing{Regards,}

\begin{document}

\makelettertitle

I am writing to apply for the position of Software Engineer - EMedia Technology (11921). 

% B.S. or M.S. in Electrical Engineering, Computer Science, Computer/Software Engineering (HD or D average preferred).

I have just completed a Bachelor of Science (Advanced) with 1st Class Honours, completing majors in Computational Science and Chemistry with a Distinction average throughout my degree.

% Demonstrated strong programming skills in C or C++ language programming;

During my Honours project I had to develop a program to extract useful data from my simulated system. For this I wrote a program in C++ \href{http://github.com/malramsay64/analysis}{github.com/malramsay64/analysis}, constantly developing and expanding on the program to add new functionality. Using this program I was able to efficiently extract data from a large number of systems which enabled me to make important discoveries which are in the process of being published.

% A genuine interest in Mobile technology, Audio, Video or E-Media development

As a Musician in the Australian Army Reserves the development of mobile audio and video technologies is interesting to me from the point of view of research. It is a side project in this position, done mostly in my own time which demonstrates my interest in the development of Audio and Video technologies. I have been producing music videos for YouTube, the most notable being a cover of John Schumann's (Red Gum) "I was Only 19" \href{https://youtu.be/U7LAo9klSRk}{youtu.be/U7LAo9klSRk} which was one of the most watched videos on ANZAC day.

% High level of technical English writing skills

At the completion of my Honours year I had to submit a Thesis explaining the major results of my research during the year. In this thesis I had to effectively communicate in writing the highly technical aspects of my project in a way that was accessible to a general scientific audience, while retaining the specificity and detail required to replicate my results. Along with my thesis I have also published two scientific papers communicating my results to scientists around the world.

% A Quick learner

During my Honours project I was was required to use a wide array of computational tools and programs that I had previously not had experience using. During the course of my Honours project I very quickly became proficient using these tools, heavily incorporating C++, Git, GNU Make and Gnuplot into the code base of my project while previously not having used any of them.


\makeletterclosing

\end{document}
