\input{../preamble.tex}


%\recipient{<Company>}{<Address>}
\recipient{~}{~}
\date{\today}
\opening{Dear Joel,}
\closing{Regards,}

\begin{document}

\makelettertitle

I am writing to apply for the role of Mathematician - Data Modelling - C++/R- Junior/Mid Level as advertised on Seek. My science background and experience in modelling and algorithms provides me with the necessary experience for this role.

In the completion of my Computational Science Major I developed experience finding numerical solutions to a variety of partial differential equations used to predict and model scientific systems. In particular I was concerned with finding solutions to the Schr\"odinger equation, from which all of Chemistry can be predicted given enough time and computing power.

I have recently completed my Bachelor of Science (Honours) majoring in both Chemistry and Computational Science. My Honours project was in the field of Computational Chemistry, modelling long timescale crystal formation. I attained 1st Class Honours and maintained a Distinction average throughout my undergraduate degree.

My Honours project was written primarily in C++ (\href{http://github.com/malramsay64/analysis}{github.com/malramsay64/analysis}) requiring modular code with significant flexibility to enable rapid development as we learnt more about the systems being studied and had new questions with new analyses. I also have experience using python, using it to generate input files and simulation parameters where quick and easy code development was more important than computational speed.

I have no prior experience using R, however I have experience in a number of programming languages which makes learning new languages a quick process. During my honours year I was required to use GNU Make, Gnuplot, and C++. Within a month I was proficient in all languages.

In my role as Musician in the Australian Army Reserve I am currently undertaking the courses required for promotion to Corporal, a position that requires me to have sufficient communication skills to communicate effectively, passing information up and down the chain of command.

My skills presenting have developed significantly recently, along with presenting my research as the final assessment of my Honours project I have been demonstrating 1st year Chemistry laboratories. This has required me to present the skills and information required to successfully complete the experiment to a new group of students each week.

I thank you for your consideration of my application and look forward to hearing from you.

\makeletterclosing

\end{document}
