\input{../preamble.tex}


%\recipient{<Company>}{<Address>}
\recipient{~}{~}
\date{\today}
\opening{Dear Sir/Madam,}
\closing{Regards,}

\begin{document}

\makelettertitle

I am writing to you to apply for the position of Software Engineer/Modeller - Operations Research as advertised on Seek.

Woking on my Honours project in simulations of large chemical systems I have developed many skills that are important to this role. Much of the programming for the project was done in C++, driven by the computational complexity of the project. During the project I was required to perform many optimisations in algorithms to bring the running time into a reasonable range, making the most of the processing and memory capabilities of the workstations I was using. This optimisation required me to have an in depth knowledge of both the computational system and the simulation system to identify modules of the codebase that were creating a bottleneck on the systems I was using.

Along with my experience with simulation systems my personal skills and initiative are also suitable for this role. I currently hold the rank of Musician in the Australian Army Reserve as a member of the 1st/15th RNSWL Band. In this role I took the initiative to produce a music video to John Schumann's "\emph{I was Only 19}" as a tribute to those who have gone before us. This video became one of the most watched YouTube videos on ANZAC day. This role in the Army Reserve also demonstrates my communication skills, I am currently undertaking the courses required for promotion to Corporal which requires me to be able to effectively lead a section of troops in a combat situation.

I thank you for considering my application and look forward to hearing from you.

\makeletterclosing

\end{document}
