%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%-------------------------------------------------------------------------------

\cvsection{Professional Experience}
% {environment} {Job Title} {Organisation} {Location} {Dates}
\begin{cventry}{Senior Data Scientist} {Cognizant}{}{Jul 2022 - Present}
  \textbf{Healthcare Client}

  Provided expertise and strategic insights in a consulting role, 
  managing a complex set of business, stakeholder, and regulatory requirements.

  \begin{itemize}
    \item Developed thorough overview of Data Privacy requirements for healthcare data.
    \item Facilitated design thinking workshops to elicit use cases from a range of stakeholders.
    \item Designed a combination of technical and non-technical solutions to meeting all the requriements.
    \item Developed a long term roadmap of value drivers to demonstate early value with a path to unlocking additional value.
    \item Collaborated across the business to bring diverse expertise and input to the project.
  \end{itemize}

  \textbf{Large Mining Client}

  Led a project working with key stakeholders across the business to reduce the impact of fatigue on safety.
  \begin{itemize}
    \item Provided Data Architecture support, ensuring appropriate privacy, security, and governence controls were in place.
    \item Used NLP to drive insights from a range of unstructured data.
    \item Utilized advanced statistical and machine learning techniques to deliver data-driven insights and solutions for clients.
    \item Presented findings, recommendations, and modelling to senior leadership and client teams, 
      leading to significant changes in business processes.
    % \item Provided timely fix to compute environment where vedor support was unable to help.
    \item Mentored junior associates and provided training on software engineering, statistical and machine learning concepts.
    \item Stayed up-to-date with the latest trends and technologies in the data science industry, incorporating them into project work where applicable.
  \end{itemize}
\end{cventry}

% {environment} {Job Title} {Organisation} {Location} {Dates}
\begin{cventry}{Data Consultant} {ASG Group}{}{Aug 2021 - Jul 2022}
  Malcolm was a key member of the ASG Data Practice,
  providing mentoring and technical expertise.
  In this role Malcolm was a key member of the ASG Labs project, 
  bringing data to life through proof of concept demonstrations.

  \textbf{SA Power Networks}

  \begin{itemize}
    \item Engaged with SA Power Networks to build out their data analytics pipeline and data lake.
    \item Led a technical team as part of an Agile project building reports for regulatory submissions.
    \item Worked at all levels of the Azure data analytics stack (Data Factory, Data Lake, Synapse, Azure SQL, Databricks).
    \item Established best practices for data management, design patterns, support, and cloud tool usage.
    \item Built Machine Learning Workflows within Databricks with an emphasis on data provenance and model reproducibility.
  \end{itemize}

\end{cventry}

\pagebreak
% {environment} {Job Title} {Organisation} {Location} {Dates}
\begin{cventry}{Software Engineer (Machine Learning)}{Adelaide MRI}{}{Dec 2020 - Jul 2021}
  Malcolm was part of a small team developing an internal web applicaiton
  to aid Doctors in writing medical imaging reports.
  Malcolm integrated a Maching Learning based recommendation engine
  into this reporting application,
  resulting in an improved the user experience and
  reducing the time taken to write them. 
  \begin{itemize}
    \item Developed Machine Learning pipelines to provide recommendations
      during the report writing process, reducing time spent
      writing reports by 21\%.
    \item Optimised common database queries, reducing the execution time by
      up to 90\%.
    \item Responsible for architecting solutions
      within the python back-end, including;
      designing database models in SQLAlchemy,
      designing RESTful APIs,
      optimising API performance,
      and incorporating security updates into the development process.
    \item Mentored graduate students in applying programming and data science
      best practices.
  \end{itemize}
\end{cventry}

% {environment} {Job Title} {Organisation} {Location} {Dates}
\begin{cventry}{eResearch Trainer, eResearch Training Administrator}{Intersect Australia}{}{Oct 2018 - Dec 2020}
  Malcolm worked at Intersect to develop and deliver training 
  for a range of programming tools
  targeted to researchers at Universities across Australia.
  Malcolm worked at all stages of the training process, 
  includign the design of content, 
  the preparation of material, managing attendees, 
  content delivery, and review of course performance.
  \begin{itemize}
    \item Developed and documented best practices for delivering Online
      training for programming languages during COVID-19 resulting in an
      18 point Net Promotor Score improvement over 
      the same suite of courses delivered in person.
    \item Developed and presented a webinar
      \chref{https://youtu.be/ViUIXTIVCvs}
      {"A Showcase of Data Analysis in Python and R: A case study using COVID-19 data"}
      demonstrating best practices in data analysis on a dataset.
    \item Delivered online training courses across a range of eResearch topics
      including Python, R, Julia, Git, SQL, MATLAB, and HPC.
    \item 100\% Net Promoter Score when runnning Programming using Julia and Programming using R.
  \end{itemize}
\end{cventry}

% {environment} {Job Title} {Organisation} {Location} {Dates}
\begin{cventry}{Co-Founder, Chief Scientist}{FluroSat}{}{Nov 2016 - Jun 2017}
  Malcolm Co-Founded the startup FluroSat, 
  implementing remote sensing and image processing techniques 
  from academic research to target key decision points 
  within the agricultural value chain.
  \begin{itemize}
    \item Implemented scalable workflows for processing remote sensing data on AWS.
    \item Developed tools for image processing and analysis in Python.
    \end{itemize}
  \textbf{Achievements}
  \begin{itemize}
      \item Portfolio company in the Muru-D accelerator program
      \item Best Team, Cicada Innovations Nobel Gala Dinner
      \item Finalist, World Bank Big Data Challenge
  \end{itemize}
\end{cventry}

\cvsection{Presentations}

\begin{cventry}
  {Navigating the intersection of data, security, and privacy in the age of smart cities}
  {Australian Cyber Conference}
  {Melbourne, Australia}
  {Oct. 2023}
  {Introducing the risks and privacy implications that exist within IoT devices
  and how they manifest within a smart city.}
\end{cventry}

\begin{cventry}
  {How long will it take to get through Airport Security?}
  {PyCon AU}
  {Adelaide, Australia}
  {Aug. 2023}
  {Demonstration of using mathematical models to understand how long we can expect to be waiting
  to get through airport security at any point of the day.}
\end{cventry}

\begin{cventry}
  {Optimising the Learning Experience for Researchers at all Levels}
  {eResearch Australasia}
  {Virtual}
  {Nov. 2020}
  {Providing an overview of the types of reaserchers that are seeking training in new technologies
  and how Intersect has been adjusting it's course material to cater for these different groups.}
\end{cventry}

\cvsection{Education}

\begin{cventry}
  {Doctor of Philosophy (PhD)} % job title
  {The University of Sydney} % organization
  {} % location
  {2015 - 2020} % date(s)
  Malcolm used a combination of statistical mechanics and data science to
  study the translational and rotational dynamics
  of small molecules in the liquid phase.
  He used High Performace Computing
  including MPI and GPU Compute
  to run long timescale computer simluations for analysis.
  \begin{itemize}
    \item Created interactive dashboard in python for analysis of simulations
      combining Bokeh and scikit-learn for real-time machine-learning analysis.
    \item Used infrastructure as code to define reproducible simulation environments
      using Ansible and Docker.
    \item Developed optimised data processing tools in Python, Cython, C++, and Rust,
      using software development best practices to ensure correctness of results.
    \item Built data lake and processing pipeline for the analysis of 10 TB of data.
    \item Designed effective data visualisations for complex datasets.
  \end{itemize}
  \textbf{Achievements}
  \begin{itemize}
    \item Winning team, Inventing the Future Competition 2016.
    \item Finalist, Merck Innovation Challenge 2018.
    \item Journal of Materials Chemistry C Poster Prize 2018.
  \end{itemize}
\end{cventry}

% \begin{cventry}
%   {Bachelor of Science (Advanced) Honours} % job title
%   {The University of Sydney} % organization
%   {} % location
%   {2010 - 2015} % date(s)
%   In his Honours thesis,
%   Malcolm used molecular dynamics simulations of small rigid molecules
%   to investigate the effect of shape on structural and dynamic properties.

%   \textbf{Achievements}
%   \begin{itemize}
%     \item Completed with \nth{1} Class Honours and \nth{1} in his cohort.
%     \item Received the Walter J Moore Honours Scholarship for academic merit in Honours.
%     \item Sydney Abroad International Exchange Scholarship.
%     \item Dean of Science Undergraduate Exchange Scholarship.
%     \item Received Levy Scholarship for achievement in \nth{1} year chemistry.
%     \item Undertook research through the Summer Scholarship Program.
%   \end{itemize}
% \end{cventry}

\cvsection{Software Skills}

\begin{cvskills}

\cvskill
  {Data Science} % Category
  {Python, Numpy, Pandas, scikit-learn, LLM, GenAI, R, SQL, Julia}

\cvskill
  {Data Engineering} % Category
  {SQL, Python, Azure Data Factory, Azure Synapse, Databricks}

\cvskill
  {Backend} % Category
  {Python, Rust, flask, FastAPI}

\cvskill
  {Frontend} % Category
  {Typescript, Web Assembly (WASM), Tailwind CSS, HTMX, HTML}

\cvskill
  {Cloud} % Category
  {Docker, AWS, Azure}

\cvskill
  {Systems} % Category
  {Rust, C++, C, CUDA, MPI}

\cvskill
  {Other} % Category
  {Git, \LaTeX, Linux, MacOS}

\end{cvskills}
